---
title: "Time course sensor-based phenotyping can predict Ascochyta blight disease severity in Cicer species"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{paper}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

devtools::load_all()
```


# Results

## Disease scores

### Overview of disease indices

Average disease indices and standard deviation of control genotypes and all pots per experiment

```{r, echo = FALSE, message = FALSE, warning = FALSE}
scores <- read_scores()
make_score_table(scores)
```

```{r echo = FALSE, fig.align='center', fig.width=7, fig.height=3, dpi=96, message=FALSE, warning=FALSE}
make_control_genotypes_score_dotplot(scores)
```

```{r echo = FALSE, fig.align='center', fig.width=7, fig.height=3, dpi=96, message=FALSE, warning=FALSE}
subsets <- unique(scores$subset)
subsets |> 
  purrr::walk(\(s) {
    p <- make_score_histogram(scores, s)
    print(p)
  })
```

### Repeatability of scoring

```{r, echo = FALSE, message=FALSE}
make_scoring_repeatability_table()
```

## Evaluation of low-level trait extraction

```{r}

```

## Smoothed FGCC and lesion count

```{r}

```

## Disease index classification

### Classification of disease severity categories in main experimental pars

```{r}

```

### Within-year disease index classification performance

```{r}

```

## Early detection of disease

