---
title: "Time course sensor-based phenotyping can predict Ascochyta blight disease severity in Cicer species"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{paper}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

devtools::load_all()
```

# Materials and Methods


### Distribution of genotypes across experiments

```{r, echo = FALSE, message=FALSE}
make_genotype_distribution_table()
```


# Results

## Disease scores

### Overview of disease indices

Average disease indices and standard deviation of control genotypes and all pots per experiment

```{r, echo = FALSE, message = FALSE, warning = FALSE}
scores <- read_scores()
make_score_table(scores)
```

```{r echo = FALSE, fig.align='center', fig.width=7, fig.height=3, dpi=96, message=FALSE, warning=FALSE}
make_control_genotypes_score_dotplot(scores)
```

```{r echo = FALSE, fig.align='center', fig.width=7, fig.height=3, dpi=96, message=FALSE, warning=FALSE}
subsets <- unique(scores$subset)
subsets |> 
  purrr::walk(\(s) {
    p <- make_score_histogram(scores, s)
    print(p)
  })
```

### Repeatability of scoring

```{r, echo = FALSE, message=FALSE}
make_scoring_repeatability_table()
```

## Evaluation of low-level trait extraction

```{r}

```

## Smoothed FGCC and lesion count

### Manual pot removal due to non-germination

Pots where a maximum FGCC of 0.05 was not exceeded throughout the entire 
experiment were removed.

```{r, echo = FALSE, message=FALSE}
make_pot_removal_info_table()
```

### Experimental layout

```{r, echo = FALSE, message=FALSE, fig.width=8, fig.height=5}
plots <- make_statgenhtp_layout_plots()
```

### Single timepoint outlier removal

```{r, echo = FALSE, message=FALSE, warning=FALSE}
counts <- make_counts_of_removed_pots_at_single_timepoints(trait = "canon_fgcc")
tables <- make_pot_single_timepoint_removal_tables(counts)
htmltools::tagList(tables)
```

#### Summary of single timepoint outlier removal 

```{r}
counts
```




## Disease index classification

### Classification of disease severity categories in main experimental pars

```{r}

```

### Within-year disease index classification performance

```{r}

```

## Early detection of disease

